\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{framed}
\usepackage{amsmath}

\begin{document}

\begin{flushright}
	Name: \underline{\hspace{3cm}} \\
	MATH55 Section \underline{\hspace{0.5cm}} \\
	Homework 16 (Trees)\\
	Due Thu. 4/11
\end{flushright}

% 16. Due Thu. 4/11:  Trees
% Homework, 3rd Edition — 50.4, 50.5, 50.6, 50.11. 

\begin{framed}
	\textbf{50.4} Let $d_1, d_2,...,d_n$ be $n \geq 2$ positive integers.
	(not necessarily distinct). Prove that $d_1,...,d_n$ are the degrees of
	the vertices of a tree on $n$ vertices if and only if $\sum_{i=1}^{n}d_i = 2n-2$.
\end{framed}

\pagebreak

\begin{framed}
	\textbf{50.5} Let $e$ be an edge of a graph $G$. Prove that $e$ is not a cut
	edge if and only if $e$ is in a cycle of $G$.
\end{framed}

\pagebreak

\begin{framed}
	\textbf{50.6} Complete the proof of Theorem 50.4. That is, prove that 
	if $G$ is a graph in which any two vertices are joined by a unique path, then 
	$G$ must be a tree.
\end{framed}

\pagebreak

\begin{framed}
	\textbf{50.11} In this problem, you will develop a new proof that every tree 
	with two or more vertices has a leaf. Here is an outline for your proof.

	\textbf{a.} First prove, using strong induction and the fact that every edge of a tree
	is a cut edge (Theorem 50.5), that a tree with $n$ vertices has exactly $n - 1$ edges.
	Please note that our previous proof of this fact (Theorem 50.9) used the fact that trees have leaves;
	that is why we need an alternative proof.
	
	\textbf{b.} Use (a) to prove that the average degree of a vertex in a tree is less than 2.
	
	\textbf{c.} Use (b) to prove that every tree (with at least two vertices) has a leaf.
\end{framed}

\end{document}